The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-07-26 manuscript.Rmd
use latex `x` sign

For geographic searches, we obtained the boundaries of the Exclusive Economic Zone for the United States from marineregions.org (mrgid:8456) [@mregions]. For the Pacific Northwest, Kozloff did not specify the exact geographic extent covered by his book. We inferred a polygon that encompass part of the Oregon coast to the northern parts of Vancouver island. For the Gulf of Mexico, we used the same geographic area as the one defined in [@Tunnell2009] by modifying manually the eastern boundaries of the shape file for the Gulf of Mexico provided by marineregions.org (mrgid:4288). These geographic areas were split into 0.2°$*$0.2° quadrats that were used to query the web API of iDigBio and OBIS using the R packages ridigbio [@ridigbio-0.3.5] and robis [@robis-0.1.8] respectively. The resulting occurrences were then clipped to only include records that fell within the EEZ boundaries.

>>>>

For geographic searches, we obtained the boundaries of the Exclusive Economic Zone for the United States from marineregions.org (mrgid:8456) [@mregions]. For the Pacific Northwest, Kozloff did not specify the exact geographic extent covered by his book. We inferred a polygon that encompass part of the Oregon coast to the northern parts of Vancouver island. For the Gulf of Mexico, we used the same geographic area as the one defined in [@Tunnell2009] by modifying manually the eastern boundaries of the shape file for the Gulf of Mexico provided by marineregions.org (mrgid:4288). These geographic areas were split into 0.2° $\times$ 0.2° quadrats that were used to query the web API of iDigBio and OBIS using the R packages ridigbio [@ridigbio-0.3.5] and robis [@robis-0.1.8] respectively. The resulting occurrences were then clipped to only include records that fell within the EEZ boundaries.
